Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-06 main.tex
Added better diagram for Henry's learning of the 6

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6}
    \caption{Progresses made by Henry over one 45-minutes interaction session
    while writing ``6''.}
    \label{}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_demos}
    \caption{Henry's demonstrations for the number ``6'' (top row) and
        corresponding shapes generated by the robot. After eight demomstrations,
        Henry decided that the robot's ``6'' was good enough, and went to
    another character: in that respect, he was the one leading the learning
process of the robot.}
    \label{henry_demos}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_distances}
    \caption{Two metrics to assess the handwriting progresses: Euclidian
    distance in the Eigenspace of the number dataset (top figure) or in
cartesian space (bottom figure). Green lines represent the robot performance,
blue lines Henry's performance. The round IDs correspond to the demonstrations
pictured on Figure~\ref{henry_demos}.}
    \label{henry_distances}
\end{figure}
